The \frb\ Observing Campaign: Multi-Telescope Radio Burst and Implications for the FRB Population

### 2016-12-19 repeater-vladata.tex
added ami coauthors. reworked abstract

@@

@@

@@

@@

@@

@@

@@

\begin{abstract}
The millisecond radio transients known as Fast Radio Bursts have recently emerged as a mysterious, new class of astrophysical transient. The discovery of repeating bursts from \frb\ has shown that at least some FRBs are not cataclysmic and opened potential for studying FRB properties via a homogenous sample of bursts. The recent localization of \frb\ with the Very Large Array has helped measure its distance and a host of intrinsic properties. This localization was made with 9 bursts seen by the VLA in coordination the Arecibo, Effelsberg, and AMI-LA observatories. We present a detailed analysis of these bursts, including the first simultaneous detection of an FRB with multiple telescopes. We show that the burst spectra typically have a broad Gaussian shape on the scale of $\sim500$~MHz with fine spectral structure consistent with either scintillation or unresolved temporal structure. We present the luminosity distribution and temporal statistics for \frb\ and argue that the whole FRB population is adequately described by a single class similar to \frb. We close with thoughts on optimal strategies to make new interferometric localizations of FRBs.
\end{abstract}

@@

High-resolution dynamic spectra at 1.4~GHz have discovered spectro-temporal structure that can bias the apparent DM differently from burst to burst \citep{WEIRD}. Observations at 1.4~GHz have measured DM in the range from xx to yy pc cm$^{-3}$, which is **smaller than/consistent with** the range of observed values seen by the VLA at 3~GHz. The FRB emission process has not yet been defined, so it is not clear how the intrinsic structure can bias DM as a function of frequency. {\color{red} Laura, any input from DM at higher frequencies?}

@@

\section*{Acknowledgements}
We thank ...
This project was supported by the University of California Office of the President under Lab Fees Research Program Award 237863. The National Radio Astronomy Observatory is a facility of the National Science Foundation operated under cooperative agreement by Associated Universities, Inc.. This research made use of Astropy, a community-developed core Python package for Astronomy (Astropy Collaboration, 2013).

>>>>

\author{T.~Cantwell}
\affiliation{University of Manchester, UK}

\author{S.~H.~Carey}
\affiliation{University of Cambridge, UK}

@@

\author{K.~Grainge}
\affiliation{University of Manchester, UK}

@@

\author{J.~Hickish}
\affiliation{Dept of Astronomy and Radio Astronomy Lab, University of California, Berkeley, CA 94720, USA}
\affiliation{University of Cambridge, UK}

@@

\author{Y.~C.~Perrott}
\affiliation{University of Cambridge, UK}

@@

\author{N.~Razavi-Ghods}
\affiliation{University of Cambridge, UK}

@@

\author{A.~Scaife}
\affiliation{University of Manchester, UK}

\author{P.~Scott}
\affiliation{University of Cambridge, UK}

@@

\author{D.~Titterington}
\affiliation{University of Cambridge, UK}

@@

\begin{abstract}
The millisecond radio transients known as Fast Radio Bursts have recently emerged as a mysterious, new class of astrophysical transient. The recent localization of \frb\ has helped identify its host galaxy, measure its distance, and infer intrinsic properties that comment on the broader FRB population. We present a detailed analysis of these bursts, including the first simultaneous detection of an FRB with multiple telescopes. We show that the burst spectra typically have a broad Gaussian shape on the scale of $\sim500$~MHz with fine spectral structure consistent with either scintillation or unresolved temporal structure. We present the luminosity distribution and temporal statistics for \frb\ and argue that the whole FRB population is adequately described by a single class similar to \frb. We close with thoughts on optimal strategies to make new interferometric localizations of FRBs.
\end{abstract}

@@

High-resolution dynamic spectra at 1.4~GHz have discovered spectro-temporal structure that can bias the apparent DM differently from burst to burst \citep{WEIRD}. Observations at 1.4~GHz have measured DM in the range from xx to yy pc cm$^{-3}$, which is **smaller than/consistent with** the range of observed values seen by the VLA at 3~GHz. The FRB emission process has not yet been defined, so it is not clear how the intrinsic structure can bias DM as a function of frequency.

@@

\section*{Acknowledgements}
This project was supported by the University of California Office of the President under Lab Fees Research Program Award 237863. The National Radio Astronomy Observatory is a facility of the National Science Foundation operated under cooperative agreement by Associated Universities, Inc.. This research made use of Astropy, a community-developed core Python package for Astronomy (Astropy Collaboration, 2013).
